Semantic Satiation among Lexically Ambiguous Words: Experiment 1b
=================================================================

Acquiring the Data
------------------

We will first download the raw CSV from github and do a bit of preprocessing on it:

```{r, echo=FALSE,results='hide'}
library(lattice)
library(nlme)
library(multcomp)
```

```{r}
download.file("https://github.com/faulconbridge/semsat/raw/master/Semsat1b/Semsat1b.csv", "semsat1b.csv", "wget", extra="--no-check-certificate")
semsat1b <- read.csv("semsat1b.csv",header=TRUE,sep=",")

# Subset the data to remove all filler and incorrectly-answered items
raw <- subset(semsat1b, ((BIAS=="dominant" | BIAS=="subordinate")
              & ANSWER=="M") | (BIAS=="unrelated" & ANSWER=="C"),select=c(
                PID,BIAS,REPS,Elapsed,MS,STDEV,IQR))

# Remove participants who encountered errors
raw <- subset(raw, PID!=7 & PID != 20, select=c(PID:IQR))

# Identify which variables should be treated as factors
raw <- within(raw, {
  BIAS <- factor(BIAS)
  REPS <- factor(REPS)
  PID <- factor(PID)
})

# Subset the data to include all MS response times
raw.MS <- subset(raw, select=c(PID:MS))
raw.MS <- na.omit(raw.MS)

# Subset the data to include all MS response times
# with outliers (more than 3sd deviation) removed
raw.stdev <- subset(raw, select=c(PID:Elapsed,STDEV))
raw.stdev <- na.omit(raw.stdev)
```

We can now fit a linear mixed-effects model to our data:
```{r}
raw.stdev$REPS <- factor(raw.stdev$REPS)

time.linear <- lme(STDEV ~ BIAS * REPS * Elapsed,
  random = list(PID = pdDiag(~ Elapsed)), na.action=na.omit, data = raw.stdev)
```

This model gives:
```{r,echo=FALSE}
summary(time.linear)
anova(time.linear)
```

We can perform post-hoc tests on item bias:
```{r}
l2 <- glht(time.linear, linfct = mcp(BIAS = "Tukey"))
summary(l2)
```

Finally, we can visualize these two main effects (i.e., those of meaning bias and of time elapsed between study and test phases). Unrelated items are illustrated in blue; subordinate in red; and dominant in green.

```{r,echo=FALSE}
fitted <- fitted(time.linear, level=0)

with(raw.stdev, plot(Elapsed[BIAS=="dominant"], fitted[BIAS=="dominant"], ylim = c(500, 2000),
  xlab = "time", ylab = "predicted", type = "b", col = "green"))
with(raw.stdev, points(Elapsed[BIAS=="subordinate"], fitted[BIAS=="subordinate"],
  pch = 4, type = "b", col = "red"))
with(raw.stdev, points(Elapsed[BIAS=="unrelated"], fitted[BIAS=="unrelated"],
  pch = 16, type = "b", col = "blue"))
```