Semantic Satiation among Lexically Ambiguous Words: Experiment 1
================================================================

Acquiring the Data
------------------

We will first (1) download the raw CSV from github; (2) convert the relevant variables---meaning bias, repetitions, relatedness, and participant ID---to factors; and (3) create three subsets of the data: one using the full dataset, one using a dataset with outliers $\pm$ 3 standard deviations removed, and a third with outliers more than 1.5 times the IQR above Q3 or below Q1 removed. We will then drop any null values from the dependent variable (MS response time) column.

```{r, cache=TRUE}
download.file("https://raw.githubusercontent.com/faulconbridge/semsat/master/Semsat1a/SemSat1a_compiled.csv", "semsat1a.csv", "wget", extra="--no-check-certificate")
semsat1 <- read.csv("semsat1.csv",header=TRUE,sep=",")

# Makes a copy of our data
raw <- semsat1

# treats our within subjects variables as factors
# renames a couple of ugly variables
raw <- within(raw, {
  BIAS <- factor(BIAS)
  RELATEDNESS <- factor(RELATEDNESS)
  REPS <- factor(REPS)
  PID <- factor(PID)
  STDEV <- MS.3.STDEV
})

# strips out all filler items and incorrect responses
raw <- subset(raw, (BIAS=="dominant" | BIAS=="subordinate") & 
                ((RELATEDNESS=="related" & ANSWER=="M") |
                (RELATEDNESS=="unrelated" & ANSWER=="C")),
              select=c(PID,BIAS,RELATEDNESS,REPS,
                       ANSWER,MS,STDEV,IQR))

raw.mean <- aggregate(raw$MS,
                      by=list(raw$PID,raw$BIAS,
                              raw$RELATEDNESS,raw$REPS),
                      FUN='mean')
colnames(raw.mean) <- c("PID","BIAS","RELATEDNESS","REPS","MS")

# subsets the data to remove any null values
# in the RTs trimmed to 3 standard deviations
raw.stdev <- subset(raw,select=c(PID,BIAS,RELATEDNESS,
                                 REPS,ANSWER,STDEV))
raw.stdev <- na.omit(raw.stdev)
raw.mean.stdev <- aggregate(raw.stdev$STDEV,
                            by=list(raw.stdev$PID,raw.stdev$BIAS,
                                    raw.stdev$RELATEDNESS,raw.stdev$REPS),
                            FUN='mean')
colnames(raw.mean.stdev) <- c("PID","BIAS","RELATEDNESS","REPS","STDEV")

# same thing trimming at +- 1.5 times the IQR
raw.iqr <- subset(raw,select=c(PID,BIAS,RELATEDNESS,
                                 REPS,ANSWER,IQR))
raw.iqr <- na.omit(raw.iqr)
raw.mean.iqr <- aggregate(raw.iqr$IQR,
                          by=list(raw.iqr$PID,raw.iqr$BIAS,
                                  raw.iqr$RELATEDNESS,raw.iqr$REPS),
                          FUN='mean')
colnames(raw.mean.iqr) <- c("PID","BIAS","RELATEDNESS","REPS","IQR")
```

Performing the Analyses
-----------------------

```{r,echo=c(1:5),results='asis'}
raw.aov <- with(raw.mean, aov(MS~BIAS*RELATEDNESS*REPS+
                             Error(PID)))

stdev.aov <- with(raw.mean.stdev, aov(STDEV~BIAS*RELATEDNESS*REPS+
                                   Error(PID)))

iqr.aov <- with(raw.mean.iqr, aov(IQR~BIAS*RELATEDNESS*REPS+
                               Error(PID)))

library(xtable)
xt <- xtable(summary(raw.aov))
xt2 <- xtable(summary(stdev.aov))
xt3 <- xtable(summary(iqr.aov))
```

### ANOVA of the untrimmed data ###
```{r,echo=FALSE,results='asis'}
print(xt, type="html")
```

### ANOVA of the stdev-trimmed data ###
```{r,echo=FALSE,results='asis'}
print(xt2, type="html")
```

### ANOVA of the IQR-trimmed data ###
```{r,echo=FALSE,results='asis'}
print(xt3, type="html")
```

We can visualize these differences as:
```{r,fig.width=21,echo=FALSE}
layout(matrix(c(1,2,3),1,3))
with(raw.stdev, interaction.plot(REPS,RELATEDNESS,STDEV,
                                 trace.label=deparse(substitute(trace.factor))))
with(raw.stdev, interaction.plot(REPS,BIAS,STDEV,
                                 trace.label=deparse(substitute(trace.factor))))
with(raw.stdev, interaction.plot(RELATEDNESS,BIAS,STDEV,
                                 trace.label=deparse(substitute(trace.factor))))
```

And we can more formally conduct follow-up tests where appropriate. First, we will look at the bias by relatedness interaction:
```{r,echo=FALSE}
domrel <- subset(raw.mean.stdev, RELATEDNESS=="related" & BIAS=="dominant",select=c(STDEV))
domunrel <- subset(raw.mean.stdev, RELATEDNESS=="unrelated" & BIAS=="dominant",
                 select=c(STDEV))
subrel <- subset(raw.mean.stdev, RELATEDNESS=="related" & BIAS=="subordinate",
                 select=c(STDEV))
subunrel <- subset(raw.mean.stdev, RELATEDNESS=="unrelated" & BIAS=="subordinate",
                   select=c(STDEV))

t.test(domrel,domunrel)
t.test(domrel,subrel)
t.test(subrel,subunrel)
t.test(domunrel,subunrel)
```

Next, the relatedness by repetition interaction:
```{r,echo=FALSE}
relshort <- subset(raw.mean.stdev, RELATEDNESS=="related" & REPS=="short",
                   select=c(STDEV))
rellong <- subset(raw.mean.stdev, RELATEDNESS=="related" & REPS=="long",
                   select=c(STDEV))
unrelshort <- subset(raw.mean.stdev, RELATEDNESS=="unrelated" & REPS=="short",
                   select=c(STDEV))
unrellong <- subset(raw.mean.stdev, RELATEDNESS=="unrelated" & REPS=="long",
                  select=c(STDEV))

t.test(relshort,rellong)
t.test(relshort,unrelshort)
t.test(rellong,unrellong)
t.test(unrelshort,unrellong)
```