Analysis of E1a and E2 data with various cutoffs
================================================

Experiment 1a
-------------

```{r,imports, echo=FALSE, results="hide"}
library(nlme)
library(psych)
library(xtable)

download.file("https://github.com/faulconbridge/semsat/raw/master/Semsat1a/semsat1a.csv", "semsat1a.csv", "wget", extra="--no-check-certificate")
semsat1a <- read.csv("semsat1a.csv",header=TRUE,sep=",")

# Makes a copy of our data
raw <- semsat1a

# treats our within subjects variables as factors
# renames a couple of ugly variables
raw <- within(raw, {
  BIAS <- factor(BIAS)
  RELATEDNESS <- factor(RELATEDNESS)
  REPS <- factor(REPS)
  PID <- factor(PID)
  STDEV <- MS.3.STDEV
})

raw <- subset(raw, BIAS!="filler", select=c(PID,BIAS,RELATEDNESS,REPS,
                       ANSWER,MS,STDEV,IQR))
```

First, our analyses with no data removed. (I.e., all incorrect responses, RTs < 200ms, and high RTs are included):
```{r,untrimmed, echo=FALSE, results="asis"}
untrimmed.mean <- aggregate(raw$MS,
                      by=list(raw$PID,raw$BIAS,
                              raw$RELATEDNESS,raw$REPS),
                      FUN='mean')
colnames(untrimmed.mean) <- c("PID","BIAS","RELATEDNESS","REPS","MS")

untrimmed.aov <- with(untrimmed.mean,aov(MS ~ BIAS*RELATEDNESS*REPS + Error(PID / (BIAS*RELATEDNESS*REPS))))
print(xtable(summary(untrimmed.aov)),type="html")
```

Now with only correct responses:
```{r,correct,echo=FALSE,results="asis"}
correct <- subset(raw, (BIAS=="dominant" | BIAS=="subordinate") & 
                ((RELATEDNESS=="related" & ANSWER=="M") |
                (RELATEDNESS=="unrelated" & ANSWER=="C")),
              select=c(PID,BIAS,RELATEDNESS,REPS,
                       ANSWER,MS,STDEV,IQR))

correct.mean <- aggregate(correct$MS,
                      by=list(correct$PID,correct$BIAS,
                              correct$RELATEDNESS,correct$REPS),
                      FUN='mean')
colnames(correct.mean) <- c("PID","BIAS","RELATEDNESS","REPS","MS")

correct.aov <- with(correct.mean,aov(MS ~ BIAS*RELATEDNESS*REPS + Error(PID / (BIAS*RELATEDNESS*REPS))))
print(xtable(summary(correct.aov)),type="html")
```

Now with the errant <200ms RTs removed:
```{r,low-RT, echo=FALSE, results="asis"}
lowtrim <- subset(correct, MS>200, select=PID:IQR)
lowtrim.mean <- aggregate(lowtrim$MS,
                      by=list(lowtrim$PID,lowtrim$BIAS,
                              lowtrim$RELATEDNESS,lowtrim$REPS),
                      FUN='mean')
colnames(lowtrim.mean) <- c("PID","BIAS","RELATEDNESS","REPS","MS")

lowtrim.aov <- with(lowtrim.mean,aov(MS ~ BIAS*RELATEDNESS*REPS + Error(PID / (BIAS*RELATEDNESS*REPS))))
print(xtable(summary(lowtrim.aov)),type="html")
```

Next we will trim the data to $\pm$3sd:
```{r,sd,echo=FALSE,results="asis"}
stdev <- subset(lowtrim, select=c(PID:REPS,STDEV))
stdev <- na.omit(stdev)
stdev.mean <- aggregate(stdev$STDEV,
                      by=list(stdev$PID,stdev$BIAS,
                              stdev$RELATEDNESS,stdev$REPS),
                      FUN='mean')
colnames(stdev.mean) <- c("PID","BIAS","RELATEDNESS","REPS","MS")

stdev.aov <- with(stdev.mean,aov(MS ~ BIAS*RELATEDNESS*REPS + Error(PID / (BIAS*RELATEDNESS*REPS))))
print(xtable(summary(stdev.aov)),type="html")
```

Finally, we can use the alternate IQR cutoff:
```{r,iqr,echo=FALSE,results="asis"}
IQR <- subset(lowtrim, select=c(PID:REPS,IQR))
IQR <- na.omit(IQR)
IQR.mean <- aggregate(IQR$IQR,
                      by=list(IQR$PID,IQR$BIAS,
                              IQR$RELATEDNESS,IQR$REPS),
                      FUN='mean')
colnames(IQR.mean) <- c("PID","BIAS","RELATEDNESS","REPS","MS")

IQR.aov <- with(IQR.mean,aov(MS ~ BIAS*RELATEDNESS*REPS + Error(PID / (BIAS*RELATEDNESS*REPS))))
print(xtable(summary(IQR.aov)),type="html")
```

Experiment 2 Analyses
---------------------

```{r,imports2, echo=FALSE, results="hide"}
download.file("https://github.com/faulconbridge/semsat/raw/master/Semsat2/semsat2.csv", "semsat2.csv", "wget", extra="--no-check-certificate")
semsat2 <- read.csv("semsat2.csv",header=TRUE,sep=",")

raw <- semsat2

# Strip out participants who encountered bugs during the experiment
# and all filler items
raw <- subset(raw, PID!=57 & PID!=42 & PID!=14 &
                BIAS!="RELATED FILLER" & BIAS!="UNRELATED FILLER",
                select=c(PID,BIAS,REPS,HomType,ANSWER,MS,MS.3.STDEV,MS.IQR))

# Specify which variables should be treated as factors
raw <- within(raw, {
  BIAS <- factor(BIAS)
  HomType <- factor(HomType)
  REPS <- factor(REPS)
  PID <- factor(PID)
  STDEV <- MS.3.STDEV
  IQR <- MS.IQR
})

```

First, our analyses with no data removed. (I.e., all incorrect responses, RTs < 200ms, and high RTs are included):
```{r,untrimmed2, echo=FALSE, results="asis"}
untrimmed.mean <- aggregate(raw$MS,
                      by=list(raw$PID,raw$BIAS,
                              raw$HomType,raw$REPS),
                      FUN='mean')
colnames(untrimmed.mean) <- c("PID","BIAS","HomType","REPS","MS")

untrimmed.aov <- with(untrimmed.mean,aov(MS ~ BIAS*HomType*REPS + Error(PID / (BIAS*HomType*REPS))))
print(xtable(summary(untrimmed.aov)),type="html")
```

Now with only correct responses:
```{r,correct2,echo=FALSE,results="asis"}
correct <- subset(raw, (BIAS=="dominant" & ANSWER=="M") |
                (BIAS=="subordinate" & ANSWER=="M") |
                (BIAS=="unrelated" & ANSWER=="C"),
              select=c(PID,BIAS,HomType,REPS,
                       ANSWER,MS,STDEV,IQR))

correct.mean <- aggregate(correct$MS,
                      by=list(correct$PID,correct$BIAS,
                              correct$HomType,correct$REPS),
                      FUN='mean')
colnames(correct.mean) <- c("PID","BIAS","HomType","REPS","MS")

correct.aov <- with(correct.mean,aov(MS ~ BIAS*HomType*REPS + Error(PID / (BIAS*HomType*REPS))))
print(xtable(summary(correct.aov)),type="html")
```

Now with the errant <200ms RTs removed:
```{r,low-RT2, echo=FALSE, results="asis"}
lowtrim <- subset(correct, MS>200, select=PID:IQR)
lowtrim.mean <- aggregate(lowtrim$MS,
                      by=list(lowtrim$PID,lowtrim$BIAS,
                              lowtrim$HomType,lowtrim$REPS),
                      FUN='mean')
colnames(lowtrim.mean) <- c("PID","BIAS","HomType","REPS","MS")

lowtrim.aov <- with(lowtrim.mean,aov(MS ~ BIAS*HomType*REPS + Error(PID / (BIAS*HomType*REPS))))
print(xtable(summary(lowtrim.aov)),type="html")
```

Next we will trim the data to $\pm$3sd:
```{r,sd2,echo=FALSE,results="asis"}
stdev <- subset(lowtrim, select=c(PID:REPS,STDEV))
stdev <- na.omit(stdev)
stdev.mean <- aggregate(stdev$STDEV,
                      by=list(stdev$PID,stdev$BIAS,
                              stdev$HomType,stdev$REPS),
                      FUN='mean')
colnames(stdev.mean) <- c("PID","BIAS","HomType","REPS","MS")

stdev.aov <- with(stdev.mean,aov(MS ~ BIAS*HomType*REPS + Error(PID / (BIAS*HomType*REPS))))
print(xtable(summary(stdev.aov)),type="html")
```

Finally, we can use the alternate IQR cutoff:
```{r,iqr2,echo=FALSE,results="asis"}
IQR <- subset(lowtrim, select=c(PID:REPS,IQR))
IQR <- na.omit(IQR)
IQR.mean <- aggregate(IQR$IQR,
                      by=list(IQR$PID,IQR$BIAS,
                              IQR$HomType,IQR$REPS),
                      FUN='mean')
colnames(IQR.mean) <- c("PID","BIAS","HomType","REPS","MS")

IQR.aov <- with(IQR.mean,aov(MS ~ BIAS*HomType*REPS + Error(PID / (BIAS*HomType*REPS))))
print(xtable(summary(IQR.aov)),type="html")
```